Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-08-18 workflow/workflow.Rmd
try plot with ercc

```{r}
# added chunk of code
library(scater)
sce <- calculateQCMetrics(
    dataObj,
    feature_controls = list(
        ERCC = isSpike(sce, "ERCC")
    )
)
cData <- colData(sce)
cData <- as.data.frame(cData)
ggplot(cData, 
       aes(x = total_counts, 
           y = total_counts_ERCC,
           col = batch)) + 
  geom_point()
```

>>>>

```{r}
# added chunk of code
library(scater)
sce <- calculateQCMetrics(
    dataObj,
    feature_controls = list(
        ERCC = isSpike(dataObj, "ERCC")
    )
)
cData <- colData(sce)
cData <- as.data.frame(cData)
ggplot(cData, 
       aes(x = total_counts, 
           y = total_counts_ERCC,
           col = batch)) + 
  geom_point()
```
